---
title: "BAWL-R Extraction"
author: "Thomas Verliefde"
date: "2018/12/04"
output: html_document
---

# Issue:

## writing the files results, at the end, in an additional \n
## Should look into fixing this, when I have the time
## Also, each word should have only the first word capitalized.
## Currently, these issues are fixed manually


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
rm(list=ls())
require(readxl)
require(stringr)
require(tidyverse)
require(tidyselect)
require(magrittr)
```

```{r import, options}

bawlR <- "BAWL-R.xls" %>% read_excel %>%
  mutate(
    WORD_CLASS = recode(
      WORD_CLASS,
      "N" = "NOUN",
      "V" = "VERB",
      "A" = "ADJ"
    )
  )

```

```{r explore letter range, options}

bawlR %>% mutate(LETTERS = case_when(
    LETTERS <= 4 ~ "[,4]",
    LETTERS <= 7 ~ "[5,7]",
    LETTERS >= 8 ~ "[8,]"
  )) %>% count(WORD_CLASS,LETTERS)

```

```{r valence, options}

bawlR %>% group_by(WORD_CLASS) %>% summarize(min(EMO_MEAN),max(EMO_MEAN),sd(EMO_MEAN))

```





```{r previously used, options}

nounsPos <- c("mut", "lust", "glück", "freude")
nounsNeg <- c("leid", "ärger", "furcht", "trauer")

adjPos <- c("frei", "klug", "treu", "gesund", "beliebt", "ehrlich", "herzlich", "friedlich")
adjNeg <- c("blöd", "dumm", "fies", "brutal", "grausam", "neidisch", "peinlich", "widerlich")

kathi <- bawlR %>% filter(
  WORD_LOWER %in% c(nounsPos,nounsNeg,adjPos,adjNeg)
) %>% mutate(
  VAL = case_when(
    EMO_MEAN < 0 ~ 'Neg',
    EMO_MEAN > 0 ~ 'Pos'
  )
)
```

```{r kathi, options}

kathi %>% filter(`Ftot/1MIL` >= 10) %>% group_by(VAL) %>% summarize(
  mean(EMO_MEAN),max(EMO_MEAN),min(EMO_MEAN),sd(EMO_MEAN),
  mean(AROUSAL_MEAN),max(AROUSAL_MEAN),min(AROUSAL_MEAN),sd(AROUSAL_MEAN),
  mean(`Ftot/1MIL`),max(`Ftot/1MIL`),min(`Ftot/1MIL`),sd(`Ftot/1MIL`)
) %>% t
  
# "Neidisch" only has a Ftot/1MIL of 2, while the others are all >= 14

```

```{r selecting items, options}

adjPos <- bawlR %>% filter(
  WORD_CLASS == "ADJ",
  EMO_MEAN >= 2,
  `Ftot/1MIL` >= 10
) %T>% {
  count(.,LETTERS) %>% print
}

adjNeg <- bawlR %>% filter(
  WORD_CLASS == "ADJ",
  EMO_MEAN <= -2,
  `Ftot/1MIL` >= 10
) %T>% {
  count(.,LETTERS) %>% print
}

nounPos <- bawlR %>% filter(
  WORD_CLASS == "NOUN",
  EMO_MEAN >= 2,
  `Ftot/1MIL` >= 30
) %T>% {
  count(.,LETTERS) %>% print
}

nounNeg <- bawlR %>% filter(
  WORD_CLASS == "NOUN",
  EMO_MEAN <= -2,
  `Ftot/1MIL` >= 30
) %T>% {
  count(.,LETTERS) %>% print
}
```

Note:

We will have multiple sets of primes, to match for name length of the significant others.
As we have 4 SOs, each will get 1 matching length letter string (B,H,S,T),
and 1 matching length valenced prime (pos/neg)


```{r creating experiment textfile, options}

"Stimuli" %>% dir.create(showWarnings = FALSE)

# Strings of different sizes

set.seed(20181001); lapply(
  2:9,
  function (x) {
    replicate(
      4,
      sample(LETTERS[-c(1,5,9,15,21,25)],1) %>% paste0(
        sample(letters[-c(1,5,9,15,21,25)],x, replace=FALSE) %>% paste(collapse="")
      )
      ,
      simplify = FALSE
    )
  }
) %>% unlist %>% paste(collapse=" ") %>% write("Stimuli/experimentPrime_Str.txt")


set.seed(20181001); lapply(
  c(4,6),
  function (x) {
    replicate(
      1,
      sample(LETTERS[-c(1,5,9,15,21,25)],1) %>% paste0(
        sample(letters[-c(1,5,9,15,21,25)],x, replace=FALSE) %>% paste(collapse="")
      )
      ,
      simplify = FALSE
    )
  }
) %>% unlist %>% paste(collapse=" ") %>% write("Stimuli/practicePrime_Str.txt")

```

```{r creating experiment textfile, options}
# Pos & Neg Nouns, in binsizes: 3-4, 5-6, 7-8, 9-10

"Stimuli" %>% dir.create(showWarnings = F)

primePos <- nounPos %>% filter(LETTERS == 3 | LETTERS == 4) %>%
  filter(
    WORD == "MUT" |
      WORD == "LUST"
  ) %>% full_join(
    nounPos %>% filter(LETTERS == 5 | LETTERS == 6) %>%
      filter(
        WORD == "GLÜCK" |
          WORD == "FREUDE"
      ),by = vars_select(names(.),everything())
  ) %>% full_join(
    nounPos %>% filter(LETTERS == 7 | LETTERS == 8) %>%
      filter(
        WORD == "FRIEDEN" |
          WORD == "HOFFNUNG"
      ),by = vars_select(names(.),everything())
  ) %>% full_join(
    nounPos %>% filter(LETTERS == 9 | LETTERS == 10) %>%
      filter(
        WORD == "VERTRAUEN" |
          WORD == "WOCHENENDE"
      ),by = vars_select(names(.),everything())
  ) %>% arrange(LETTERS) %T>% {paste(.$WORD_LOWER,collapse=" ") %>% str_to_title %>% write("Stimuli/experimentPrime_Pos.txt")}

primeNeg <- nounNeg %>% filter(LETTERS == 3 | LETTERS == 4) %>%
  filter(
    WORD == "NOT" |
      WORD == "LEID"
  ) %>% full_join(
    nounNeg %>% filter(LETTERS == 5 | LETTERS == 6) %>%
      filter(
        WORD == "FEIND" |
          WORD == "STREIT"
      ),by = vars_select(names(.),everything())
  ) %>% full_join(
    nounNeg %>% filter(LETTERS == 7 | LETTERS == 8) %>%
      filter(
        WORD == "DROHUNG" |
          WORD == "ABSCHIED"
      ),by = vars_select(names(.),everything())
  ) %>% full_join(
    nounNeg %>% filter(LETTERS == 9 | LETTERS == 10) %>%
      filter(
        WORD == "GEFÄNGNIS" |
          WORD == "VERBRECHEN"
      ),by = vars_select(names(.),everything())
  ) %>% arrange(LETTERS) %T>% {paste(.$WORD_LOWER,collapse=" ") %>% str_to_title %>% write("Stimuli/experimentPrime_Neg.txt")}

# Positive and Negative Targets, 8 each, only 4 each will be used

targetPos <- adjPos %>%
  filter(
    LETTERS >= 4,
    EMO_MEAN > mean(EMO_MEAN),
    WORD != "POSITIV"
    ) %T>% {paste(.$WORD,collapse=" ") %>% write("Stimuli/experimentTarget_Pos.txt")}

targetNeg <- adjNeg %>%
  filter(
    LETTERS >= 4,
    WORD != "NEGATIV",
    WORD != "NUKLEAR",
    WORD != "SCHLECHT"
  ) %T>% {paste(.$WORD,collapse=" ") %>% write("Stimuli/experimentTarget_Neg.txt")}


```

```{r creating practice textfile, options}

"Stimuli" %>% dir.create(showWarnings = F)


# All identical to impamb2's practice words

paste("Kuss","Idee","Chance",collapse = " ") %>%
  write("Stimuli/practicePrime_Pos.txt")

paste("Mord","Angst","Sklave",collapse = " ") %>%
  write("Stimuli/practicePrime_Neg.txt")

paste("Geduldig","Zärtlich","Humorvoll","Fleissig",collapse = " ") %>%
  write("Stimuli/practiceTarget_Pos.txt")

paste("Boshaft","Korrupt","Ungerecht","Gehässig",collapse = " ") %>%
  write("Stimuli/practiceTarget_Neg.txt")

```